A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-05-23 results.tex
new examples for attr patterns

\begin{lstlisting}[language=Rust, style=colouredRust]
// G.attr.struct.add: Adding attributes to a struct
<@\textcolor{green}{++}@> #[derive(Debug, Clone)]
pub struct Call {
/// body 
}

//G.attr.struct.drop: Removing attributes from a struct
<@\textcolor{red}{--}@> #[derive(Debug, Clone)]
pub struct Call {
/// body 
}

// G.attr.struct.change: Changing an existing attribute of a struct
<@\textcolor{red}{--}@> #[derive(Debug)]
<@\textcolor{green}{++}@> #[derive(Debug, Clone)]
pub struct Call {
/// body 
}
\end{lstlisting}

\noindent\textbf{Description:} In this pattern, the attribute set of a struct changes. This modification can happen in three different ways: Adding attributes to the struct (G.attr.struct.add); Removing attributes from the struct (G.attr.struct.drop); Changing the content of an existing attribute (G.attr.struct.change). These attributes are Outer Attributes as we can find struct-related non terminals within the ASTDiff of the instances of this pattern. \\

@@

\begin{lstlisting}[language=Rust, style=colouredRust]
// G.attr.struct.field.add: Adding attributes to struct fields
#[derive(Serialize)]
pub struct Retain {
    <@\textcolor{green}{++}@> #[serde(skip_serializing_if = "is_empty")]
    pub attributes: Option<Attributes>,
}

// G.attr.struct.field.drop: Removing attributes from struct fields
#[derive(Serialize)]
pub struct Retain {
    <@\textcolor{red}{--}@> #[serde(skip_serializing_if = "Option::is_none")]
    pub attributes: Option<Attributes>,
}

>>>>

\begin{lstlisting}[language=Rust, style=colouredRust]
// G.attr.struct.add: Adding attributes to a struct
<@\textcolor{red}{--}@> #[derive(Clone, Properties)]
<@\textcolor{green}{++}@> #[derive(Clone, Properties, PartialEq)]
pub struct CounterProps {
    pub destroy_callback: Callback<()>,
}

//G.attr.struct.drop: Removing attributes from a struct
<@\textcolor{red}{--}@> #[derive(Serialize, Deserialize, Clone, PartialEq, Eq, Debug)]
<@\textcolor{green}{++}@> #[derive(Serialize, Deserialize, Clone, PartialEq, Eq)]
pub struct Subset {
    /// Invariant, maintained by `SubsetBuilder`: all `Segment`s have non-zero
    /// length, and no `Segment` has the same count as the one before it.
    segments: Vec<Segment>,
}

// G.attr.struct.change: Changing an existing attribute of a struct
<@\textcolor{red}{--}@> #[derive(Deserialize, Debug, Copy, Clone, PartialEq, Eq)]
<@\textcolor{green}{++}@> #[derive(ConfigDeserialize, Debug, Copy, Clone, PartialEq, Eq)]
pub enum SearchAction {
    SearchFocusNext,
    SearchFocusPrevious,
    SearchConfirm,
    SearchCancel,
    SearchClear,
    SearchDeleteWord,
    SearchHistoryPrevious,
    SearchHistoryNext,
}
\end{lstlisting}

\noindent\textbf{Description:} In this pattern, the attribute set of a struct changes. This modification can happen in three different ways: Adding attributes to the struct (G.attr.struct.add); Removing attributes from the struct (G.attr.struct.drop); Changing the content of an existing attribute (G.attr.struct.change). These attributes are Outer Attributes as we can find struct-related non terminals within the ASTDiff of the instances of this pattern.\\

@@

\begin{lstlisting}[language=Rust, style=colouredRust]
// G.attr.struct.field.add: Adding attributes to struct fields
#[derive(Serialize)]
pub struct Retain {
    <@\textcolor{green}{++}@> #[serde(skip_serializing_if = "Option::is_none")]
    pub attributes: Option<Attributes>,
}

// G.attr.struct.field.drop: Removing attributes from struct fields
pub struct ExpandContext<'context> {
    #[get = "pub(crate)"]
    pub registry: Box<dyn SignatureRegistry>,
    <@\textcolor{red}{--}@> #[get = "pub(crate)"]
    pub source: &'context Text,
    pub homedir: Option<PathBuf>,
}
